fdcoexist

### 2018-10-17 meta_simulations.Rmd
Add scenarios with varying A

# Actual simulation -----------------------------------------------------------
plan(multiprocess, workers = availableCores() - 2)
tictoc::tic()
normal_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

@@

@@

plot_all_k_cwm_env = all_simuls %>%
    filter(!(scenario %in% c("R75A25", "R25A75")),
           compet_status == "compet",
           env_width == "constant") %>%
    ggplot(aes(patch_optim, trait2_cwm, color = fct_rev(cor_level),
               group = interaction(cor_level, seed_number))) +
    geom_line(aes(group = interaction(cor_level, seed_number)), alpha = 1/20) +
    geom_smooth(aes(group = cor_level), se = FALSE) +
    facet_grid(rows = vars(simul), cols = vars(scenario),
               labeller = lab_compet_env) +
    scale_color_viridis_d("Correlation", labels = lab_cor) +
    labs(x = "Environment",
         y = "Trait 2 CWM",
         title = paste0("CWM <-> Env. Relationship across N = ", total_runs,
                           " sets of traits"),
         subtitle = paste0("opaque line = smoothed average\n",
                           "background lines = individual simulations")) +
    theme(panel.grid = element_blank(),
          legend.position = "top")
plot_normal_k_cwm_env

@@

>>>>

# Actual simulation -----------------------------------------------------------
plan(multiprocess, workers = availableCores())
tictoc::tic()
normal_k_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

@@

```{r normal_k_low_A}
# Competition >> Environmental filtering
# Simulation parameters --------------------------------------------------------
low_A = 2e-5
normal_k_low_A_run_char = paste0("N = ", total_runs, "; A = ", low_A, "; B = ",
                               B, "; k = ", k)

# Actual simulation -----------------------------------------------------------
tictoc::tic()
normal_k_low_A_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, given_k = k, given_A = low_A)
}, .progress = FALSE)
tictoc::toc()
```

```{r normal_k_high_A}
# Competition << Environmental Filtering
# Simulation parameters --------------------------------------------------------
high_A = 2e-3
normal_k_high_A_run_char = paste0("N = ", total_runs, "; A = ", high_A,
                                  "; B = ", B, "; k = ", k)

# Actual simulation -----------------------------------------------------------
tictoc::tic()
normal_k_high_A_simuls = future_map(seq(total_runs), function(x) {
    devtools::load_all()

    meta_simul(x, given_k = k, given_A = high_A)
}, .progress = FALSE)
tictoc::toc()
```

@@

plot_all_k_cwm_env = all_simuls %>%
    filter(!(scenario %in% c("R75A25", "R25A75")),
           compet_status == "compet",
           env_width == "constant") %>%
    mutate(simul_param = factor(simul_param, levels = c("high_k_normal_A",
                                                        "normal_k_normal_A",
                                                        "low_k_normal_A"))) %>%
    ggplot(aes(patch_optim, trait2_cwm, color = fct_rev(cor_level),
               group = interaction(cor_level, seed_number))) +
    geom_line(aes(group = interaction(cor_level, seed_number)), alpha = 1/20) +
    geom_smooth(aes(group = cor_level), se = FALSE) +
    facet_grid(rows = vars(simul_param), cols = vars(scenario),
               labeller = lab_compet_env) +
    scale_color_viridis_d("Correlation", labels = lab_cor) +
    labs(x = "Environment",
         y = "Trait 2 CWM",
         title = paste0("CWM <-> Env. Relationship across N = ", total_runs,
                           " sets of traits"),
         subtitle = paste0("opaque line = smoothed average\n",
                           "background lines = individual simulations")) +
    theme(panel.grid = element_blank(),
          legend.position = "top")
plot_normal_k_cwm_env

@@

plan(multiprocess(workers = availableCores()))
tictoc::tic()
